High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-19 notebooks/mnist.qmd
adam also working nicely

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                        # finaliser function
```

@@

```{julia}
plt, eccco_generator, ces = _plot_eccco_mnist()
display(plt)
savefig(plt, joinpath(output_images_path, "mnist_eccco.png"))
```

>>>>

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 100])
n_hidden = 128
activation = Flux.swish
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                       # number of models in ensemble
_loss = Flux.Losses.crossentropy           # loss function
_finaliser = Flux.softmax                            # finaliser function
```

@@

```{julia}
opt = Flux.Optimise.Adam(0.01)
Λ = [0.1,0.25,0.25]
use_class_loss = true

plt, eccco_generator, ces = _plot_eccco_mnist(opt=opt, λ=Λ, use_class_loss=use_class_loss)
display(plt)
savefig(plt, joinpath(output_images_path, "mnist_eccco.png"))
```
